\section{Main Components}

\subsection{Controllers}

\subsubsection{RobotController}
\textbf{Purpose}: Manages the interactions related to setting the robot's IP address and executing commands on the robot.

\textbf{Key Actions}:
\begin{itemize}
	\item \textbf{SetIp}: Allows the user to input the robot's IP address and verifies connectivity by pinging the robot.
	\item \textbf{ExecuteFunction}: Executes a specific command on the robot by function ID. This involves retrieving the command from the database and using the SSH service to execute it on the robot.
\end{itemize}

\subsubsection{DatabaseController}
\textbf{Purpose}: Handles database-related operations such as importing data from an Excel file.

\textbf{Key Actions}:
\begin{itemize}
	\item \textbf{Upload}: Provides a web interface for uploading an Excel file.
	\item \textbf{ImportData}: Parses the uploaded Excel file and inserts the data into the database. This is useful for populating the database with predefined functions and commands.
\end{itemize}

\subsubsection{FunctionsController}
\textbf{Purpose}: Manages CRUD (Create, Read, Update, Delete) operations for functions and their associated commands.

\textbf{Key Actions}:
\begin{itemize}
	\item \textbf{Index}: Lists all functions in the database, providing options to create, edit, delete, and execute functions.
	\item \textbf{Create}: Displays a form for creating a new function. This includes selecting commands and libraries associated with the function.
	\item \textbf{Edit}: Displays a form for editing an existing function and its associated commands and libraries.
	\item \textbf{Delete}: Deletes a function from the database.
	\item \textbf{Details}: Displays detailed information about a specific function, including its associated commands and libraries.
\end{itemize}

\subsection{Services}

\subsubsection{SshService}
\textbf{Purpose}: Handles SSH connections and command execution on the robot.

\textbf{Functionality}:
\begin{itemize}
	\item \textbf{SetHost}: Sets the IP address of the robot for SSH connections.
	\item \textbf{TestConnection}: Tests the SSH connection to ensure it can successfully connect to the robot.
	\item \textbf{ExecuteCommand}: Executes specified commands on the robot via SSH.
\end{itemize}

\subsubsection{RobotService}
\textbf{Purpose}: Interacts with the SSH service to execute commands on the robot.

\textbf{Functionality}:
\begin{itemize}
	\item \textbf{ExecuteCommand}: Retrieves the command associated with a given function ID from the database and executes it on the robot. If the Docker container is not already running, it starts the container before executing the command.
\end{itemize}
